Meta-analysis of fungicide application timing experiments for powdery mildew management

### 2020-03-12 06_Publication_wireframe_and_7_Questions.Rmd
writing and editing

In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop, with approximately 90% of yields exported. 
Mungbean can provide a good return for growers with a potential yield of up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potential crop yields can be limited by diseases such as powdery mildew (*Podosphaera xanthii*) by up to 40% [@Kelly2017a; @Chankaew2013]. 
Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.

@@

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
Quantitative disease resistance has been observed in some breeding lines [@Pandey2018; @Chankaew2013]. 
In Australia there are very few available powdery mildew resistant cultivars. 
Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation]. 
Because cultivar choice does not confer complete resistance to powdery mildew treating mungbean with fungicide is still required to limit yield damage when conditions for the disease are suitable.

### Previous studies - fungicide work
There is almost a complete lack of peer-reviewed experiments testing fungicide efficacy on powdery mildew in Mungbean. What information is available
Past field trials in eastern Australia have trialled a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. 
Early trials indicated to obtain maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary []. 
Some of the trialled fungicides have been registered with the APVMA [@APVMA] for treating powdery mildew in mungbean [@Kelly2017a; insert all published trials here].

@@

The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
Trials undertaken in 2013 were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
The data from the collection of trials were in different formats with varying levels of information.
Some trial data reporting means of each treatment, others we were able to obtain the complete raw data.

@@

The inclusion of trial data was set to the following criteria; an field trial testing the efficacy of demethylase inhibitors (DMI), tebuconazole or propiconazole, for powdery mildew control on mungbean in the northern grains regions of eastern Australia. 
All the trials included in this analysis were  not previously been published in peer-reviewed literature.
Some trials and results were reported online via the Grains Research and Development Corporation.

Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref].
The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease. 
Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.

>>>>

In Australia Mungbean is grown in southern Queensland and northern New South Wales as a short season summer legume crop. 
Approximately 90% of mungbean yields are exported providing good returns for growers. 
Mungbean potentially yields up to 2.3 tonnes per hectare, with a value of up to \$ 1300 a tonne [@QueenslandGovernment2019]. 
However these potential crop yields can be limited by a range of diseases[@Kelly2017a].
Powdery mildew (*Podosphaera xanthii*), for instance limits yields by up to 40% [@Chankaew2013]. 
Fortunately a number of strategies are available to be employed to reduce the damage powdery mildew inflicts on yields.

@@

Commercially available mungbean cultivars in Australia lack sufficient resistance to be used as a sole powdery mildew management strategy.
Quantitative disease resistance has been observed in some breeding lines overseas [@Pandey2018; @Chankaew2013]. 
While some quantitive resistance has been incorporated into Australian varieties there remain few powdery mildew resistant cultivars. 
Jade-AU is recommended as containing the best disease resistance to powdery mildew (moderately susceptible), and other foliar diseases, such as tan spot and halo blight [@AustralianMungbeanAssociation]. 
Because cultivar choice does not confer complete resistance to powdery mildew treating mungbean with fungicide is still required to limit yield damage when conditions for the disease are suitable.

The recent release of 'PowderyMildewMDM' a desicion support system (DSS) increases the ease for preparing a fungicide spray scheduale to manage powdery mildew. 
PowderyMildewMDM provides a cost benefit analysis to growers for spray scheduale scenarios.
The user inputs weather, crop, and economic inputs into the DSS and the app returns the probability one or two fungicide sprays would protect yields suffiently to cover the costs of the fungicide applications.

### Previous studies - fungicide work
There is almost a complete lack of peer-reviewed literature summarising fungicide efficacy on powdery mildew in Mungbean. 
Many of the experimental work has been published by funding agencies and state government extension departments. 
Past field trials in eastern Australia have trialed a range of fungicide active ingredients (table), while also attempting to evaluate the best application time for the highest efficacy [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013; @SueThompson2016; @Kelly2017a; @Thompson2016]. 
Early trials showed for a fungicide application to provide maximum efficacy a single fungicide application at first sign of the disease with another follow-up application two weeks later if necessary [@Sparks2017]. 
Some of the trialled fungicides for treating powdery mildew in mungbean have been registered with the APVMA [@APVMA; @Kelly2017a; insert all published trials here].

@@

The data for this study was obtained from through personal correspondence with colleagues and collaborating institutions.
The majority of the trials were undertaken by Malcolm Riley and Dr Sue Thompson with The Department of Agriculture and Primary industries (DAF). 
Trials undertaken in 2013 season were conducted by the Northern growers alliance [@goolhi2013; @premer2013; @Millmerran2013; @Marysmount2013].
The most recent trials from 2017 were undertaken by DAF and the University of Southern Queensland (USQ) from 2017 to 2019 (Table 1). 
The data from trials were in different formats with varying levels of information.
Some trial data reporting means of each treatment, others contained the complete raw data.

@@

The inclusion of trial data required a field trial testing the efficacy of  for powdery mildew control on mungbean in the northern grains regions of eastern Australia. 
All the trials included in this analysis were not previously been published in peer-reviewed literature.
Some trials and results were reported online via the Grains Research and Development Corporation.

Differences between each trial were likely to influence the analysis and in an effort to reduce confounding effects we only included treatments within trials which had been sprayed with one of fungcides from demethylase inhibitors (DMI) group. 
Fungicide actives from the DMI group was the main inclusion factor for the analysis which reduced the number of studies from 24 to 17 experiments. DMI fungicides which were used for experimentation for powdery mildew control on mungbean were tebuconazole and propiconazole,

Most of the studies which were used in this analysis assessed powdery mildew incidence on a 1 - 9 ordinal scale [ref].
The NGA 2013 trials reported incidence as a percentage of leaves covered by the disease at different plant heights. 
Given the ordinal scale ranked plants on the percent of foliage up the plant showing the disease, it was easy to calculate the equivalent incidence on the ordinal 1 - 9 scale.
